\section{Introduction} % (~10%)
% The introduction to your report is important. It sets the scene, showing the state of research in the tiny area relevant to your work. Make sure that you know and write down which research question you are addressing, how other people have succeeded in getting some way towards an answer, and how you are trying to potentially get further forward or replicate their results. Read the papers that you cite, to check that they say what you think.

\subsection{Design of the~robot}

\par Our robot, CycBot, was designed in Fusion~360 and fabricated using a~combination of 3D~printing and silicone molding. The~robot's body consists of a~3D-printed frame, while the~body and ears are made from Ecoflex~00-30 silicone. The~robot uses one servo motor to rotate head, three air pumps, and two air valves to control the~inflation and deflation of the~ears. To make the~robot more human-like, we cast `belly' and ears using skin-coloured silicone. To keep the~robot upright we poured small amount of hard silicone on~the~bottom of its belly. The~robot is controlled using the~Arduino~Uno microcontroller~\cite{arduino-uno}, which manages the~servo motor and air pumps/valves. The robot's behaviour is programmed to respond to human interactions, allowing it to express different emotions through ear movements and head rotations.

\par We designed our robot to show five distinct emotions: interested, happiness, annoyed and sadness. Each emotion is expressed through a~combination of ear movements and head rotations, based on the~human input. The~inflatable belly of the robot has a~pressure sensor that detects when a~human touches it and for how long.
